A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
really close to having the table formatted correctly... but not quite!

```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
Table1 <- read_csv("Data/Table1.csv")

@@

kable(Table1, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.", booktabs = T) %>%
kable_styling(latex_options = c("hold_position"))

@@

```{r Table S2, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)

TableS2 <- read_csv("Data/TableS2.csv")

kable(TableS2, format = "latex", caption = "Summary statistics of the phylogenetic signal analysis.", booktabs = T) %>%
kable_styling(latex_options = c("hold_position"))
```

>>>>

```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
Table1a <- read_csv("Data/Table1.csv")
colnames(Table1a) <- gsub("X1", "Variable", colnames(Table1a))
is.num <- sapply(Table1a, is.numeric)
Table1a[is.num] <- lapply(Table1a[is.num], round, 3)

Table1b <- read_csv("Data/TableS2.csv")
colnames(Table1b) <- gsub("X1", "Variable", colnames(Table1b))
is.num <- sapply(Table1b, is.numeric)
Table1b[is.num] <- lapply(Table1b[is.num], round, 3)

grouped <- rbind(cbind(Value="Statistic", Table1a), cbind(Value="p-values", Table1b))
tgrp <- xtabs(cbind(Cmean, I, K, K.star, Lambda) ~ Value+Variable, grouped)

table <- ftable(aperm(tgrp, c(3, 1, 2)), row.vars=c("Variable", "Value"))

@@

kable(table, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.")

@@
